HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2022-01-19 hermes_paper/hermes_ieee.tex
Minor corrections in Section 3

Due to the increasing use of social media and behaviour changes, a normalization step is applied to the raw sequences. Each fashion trend is divided by its hierarchical parent category trend. Moreover, in order to not remove the seasonality of all sequences, we deseasonalized the hierarchical parent category trend before the normalization. For instance, as displayed in Figure~\ref{fig:normalization}, the raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China. The final normalized sequence is expressed in share of category.

>>>>

Due to the increasing use of social media and behaviour changes, a normalization step is applied to the raw sequences. Each fashion trend is divided by its hierarchical parent category trend. Moreover, in order to avoid removing the seasonality of all sequences, we deseasonalized the hierarchical parent category trend before the normalization. For instance, as displayed in Figure~\ref{fig:normalization}, the raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China. The final normalized sequence is expressed in share of category.
